Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-09-05 chatbot_classification/aaai_2021/paper.tex
update experimental results and analysis

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems. In these applications,
    one  of  the  core  problems is the intention detection from a user's input.
    Then,  the  intention  with  its  associated  information  is  mapped into a
    predefined dialog logic graph, and the chatbot returns corresponding answer.
    This  is  the  main  difference  from  a  free chatbot system. The intention
    detection,  assuming  only  one  intention  in  a  user's input here, can be
    modeled  as  a  short  text  classification.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; enough training data is not trivial
    to be filtered out and labeled from tons of raw user logs with miscellaneous
    information, and generally only 10 to 20 samples per intention are available
    in  the  early  stage.  Then,  how  to  train  an  efficient model in such a
    practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification Model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. The experimental results
    show that our new model outperforms very strong baselines, BERT, RoBERTa and
    ALBERT based pretrained models by 2 percentages in average accuracy.

@@

  \section{Methodology}
  In  this  section,  we  will  describe a system of similarity model fused with
  classification  model,  named  as  SFC, in detail. We come up with 2 different
  approaches  for  implementation  of SFC system, in which joint SFC is a
  further improvement of two-stage SFC for better performance.

@@

  The   detailed   network   structure   of   two-stage   SFC  is  shown  in  Fig.
  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
  top-K  most  related class labels for sampling sentence pairs of both positive
  samples  and negative samples for stage 2. Suppose we have a training data set
  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
  is the user input query and $y_{i}$ is a single class label from a class label
  set  of  $C$  classes  in total. If we want to generate sentence pair data set
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
  similarity class label, see Equ. \ref{eq:similarity label},
  \begin{align}
    l_{j}=
    \begin{cases} \label{eq:similarity label}
      0 & y_{x}\neq y_{x'}\\
      1 & y_{x}=y_{x'}
    \end{cases}
  \end{align}
  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
  might be too time-consuming for the training process of stage 2 since we often
  have  hundreds  of class labels under task-specific chatbot scenario. Although
  we  may  only  have  a  few data points for a single class label, $M$ is still
  quite a big number.

@@

  \textbf{1.  positive  sentence pair sampling}: During the training process, we
  have  to first make sure that the ground truth class label $y_{i}$ for $x_{i}$
  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
  \mathcal{C'}$,  we  will manually add $y_{i}$ into $\mathcal{C'}$ by replacing
  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
  sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
  label as $y_{i}$ from data set $\mathcal{D}$ to form the set of sentence pairs
  with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
  x'_{1}),   1],   \dots,   [(x_{i},   x'_{P}),  1]\}$,  where  $P$  is  also  a
  hyperparameter  set  by  us  that  controls  the number of sentences we should
  sample from each class.

@@

  In  this  way,  we  can generate the sentence pair data set $\mathcal{D'}$ for
  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
  which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.

@@

  As for  stage  1,  our  SFC  system  can adapt to any auxiliary model or even
  searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
  retrieval.  In  this  paper,  however,  we  choose to fine-tune RoBERTa on our
  task-specific  data set $\mathcal{D}$ by adding a softmax classifier on top of
  it,  the  same  as  the  structure shown in Fig. \ref{Fig.1.sub.1}, for better
  overall  performance.  According  to  our  experimental  result,  RoBERTa  can
  guarantee  that  approximately  95\%  ground  truth label be included in top-5
  candidate  class  labels  with  highest  probability after being fine-tuned on
  task-specific  data set with experimental result measured by F-score at around
  0.75.  So  we use RoBERTa as encoder of classification model in our setting at
  stage 1 to ensure low limitation for the performance of stage 2.

  For single-sentence text classification tasks, given a data point $x_{i}$ with
  class  label  $y_{i}$  from  data  set  $\mathcal{D}$, RoBERTa takes the final
  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
  whole   sequence  of  $x_{i}$.  Let's  suppose  we  have  a  linear  layer  as
  ${\Phi}^C_{i}=W^Ch_{i}+b^C$,  where  $W^C$ and $b^C$ are trainable parameters,
  the    probability    score    for    $x_{i}$    can    be    calculated    as
  $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.   Then,  the  loss  for
  stage 1 classification model is shown in Equ. \ref{eq:classification loss}, in
  which  the  first  term  $\varPhi_{i,y_{i}}^C$ encourages high probability for
  prediction of the correct label $y_{i}$.

@@

  As for  stage 2, we also choose RoBERTa as the encoder for sentence pairs, as
  shown  in Fig. \ref{fig:ver.1.3}. Before sending sentence pairs to Roberta, we
  pack  sentence  pairs  into a single sequence and separate them with a special
  token  [SEP].  Roberta  will  also  add  a  learned  embedding  to every token
  indicating  whether  it belongs to the first sentence or the second one. Then,
  we  utilize  the  cross-attention  mechanism  inside RoBERTa, and then extract
  semantic relationship between 2 sentences from the output softmax layer, which
  is placed on top of the last hidden representation of the [CLS] token.

@@

  Due  to  the  fact that sentence pairs within the same class is much less than
  sentence  pairs  from  different  classes,  the  data  set  $\mathcal{D'}$  is
  imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
  to  the  loss  to eliminate the bias brought by imbalanced data, shown in Equ.
  \ref{eq:similarity loss}.

@@

  As  for top-K classification task, it shares the same sentence-pair similarity
  model   structure  with  task  1.  The  only  difference  is  that  we  add  a
  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:ver.1.3} to
  implement the classification task based on sentence-pair model.

@@

  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.

@@

      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        Dataset & Domain & \#Class & \#Samples & \#Samples/Class & Experimental Settings\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280] & [5, 10, 15, 20] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250] & [5, 10, 15] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540] & [5, 10, 15, 20] & data sampling\tabularnewline
        \hline 
      \end{tabular}
      \par
    \end{centering}
    \caption{Key statistics for experimental datasets and few shot settings}

@@

  \section{Experiments}
  In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
  datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
  effectiveness  of  the  methodology  of  multi-task  learning  and hierachical
  joint-model structure under low-data settings.

  \subsection{Datasets}
  The  datasets  used in our experiments aims to help us study low-resource text
  classification  problem  under  task-specific conversational chatbot scenario.
  Therefore,  we keep all the dataset under low-resource chatbot corpus setting,
  which  is a large number of class labels (50-250) with a few examples(5-20) in
  short  text  for  each  class, by sampling smaller subsets from the full scale
  when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}.

@@

  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
  classification  task from the extreme classification repository with full data
  containing  670,091  class  labels,  285,176  training samples and 150875 test
  samples \cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
  labels  per  training sample, we keep only the first class label for each data
  point. Besides, we also randomly sampled 250 class labels from all the classes
  that  contain only 5-15 data points. In this way, we simulate the low-resource
  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
  samples for 250 class labels.

@@

      \scalebox{0.8}{
        \begin{tabular}{|c|ccc|cccc|cccc|c|c|}

@@

          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{CLINC150}}& \multicolumn{4}{c|}{\textbf{BANKING77}}& \multicolumn{4}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
          \cline{2-14}
          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & \textbf{Full} & \textbf{Full}\tabularnewline

@@

          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.578$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
          (classification) & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
          (similarity) & & & & & & & & & & & & &\tabularnewline

@@

          two-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
          (task1 only) & & & & & & & & & & & & &\tabularnewline

@@

    \label{tbe:table2}
  \end{table*}

>>>>

  \begin{abstract}
    Task-specific  chatbot  systems has gained many important applications, such
    as  Siri, Google home, customer service systems to allievaite human's labor.
    In  this  kind  of  systems, one of the core problems is the accurate detection of
    intention  of  a  user's input. It is then mapped into a predefined chatting
    logic  graph,  and the chatbot can return reasonable answers easily. This is
    the  main  difference from a free chatbot. The intention detection, assuming
    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
    classification  problem.  In  practice,  the  number  of  intentions  can be
    hundreads of thousands, as opposed to quite limited in the tradiational text
    classification  problem,  and  the  labeled  data  is not trivial to acquire
    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
    model  in such a resource-intensive practical application in a new domain is
    critical.  In  this  work, we propose a novel model, called similairty model
    fused with classification Model (SFC), which combines a classification model
    and  a  similairty  model,  and  borrows the power of multi-task training as
    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
    The  experimental  results  show  that our new model outperforms very strong
    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
    in average accuracy.

@@

  \section{Methodology}
  In  this  section,  we  will  describe our proposed system of similarity model fused with
  classification  model,  named  as  SFC, in detail. We come up with 2 different
  approaches  for  implementation  of SFC system, in which joint SFC is a
  further improvement of two-stage SFC for better performance.

@@

  The network   structure   of   two-stage   SFC  is  composed  with  2  separate  stages  in  charge of
  different  jobs. In stage 1, we can use any auxiliary text classification model or tool to provide
  top-K  most  related class labels. These selected class labels will later be used to sample sentence pairs of both positive
  samples  and negative samples for stage 2. Then, in stage 2, we will use sentence pair similarity model to identify the class label with strongest semantic similarity to the user input sentence. Suppose we have a training dataset
  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
  is the user input query and $y_{i}$ is a single class label from a class label
  set  of  $C$  classes  in total. If we want to generate sentence pair dataset
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
  similarity class label, see Equ. \ref{eq:similarity label},
  \begin{align}
    l_{j}=
    \begin{cases} \label{eq:similarity label}
      0 & y_{x}\neq y_{x'}\\
      1 & y_{x}=y_{x'}
    \end{cases}
  \end{align}
  directly  from  original dataset $\mathcal{D}$ without any sampling strategy,
  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
  might be too time-consuming for the training process of stage 2 since we often
  have  hundreds  of class labels under task-specific chatbot scenario. Although
  we  may  only  have  a  few data points for a single class label, $M$ is still
  quite a big number.

@@

  \textbf{1.  positive  sentence pair sampling}: During the training process, we
  have  to first make sure that the ground truth class label $y_{i}$ for $x_{i}$
  is  within  the  candidate  class  label  set  $\mathcal{C'}$. If $y_{i}\notin
  \mathcal{C'}$,  we  will manually add $y_{i}$ into $\mathcal{C'}$ by replacing
  $c'_{K}$  with  $y_{i}$, since $c'_{K}$ is the least promising candidate label
  according  to  the  auxiliary  model  in stage 1. Afterwards, we will randomly
  sample  $P$  sentences  $\{x'_{0},x'_{1}, \dots, x'_{P}\}$ with the same class
  label as $y_{i}$ from dataset $\mathcal{D}$ to form the set of sentence pairs
  with   positive   label  $\mathcal{P'}_{i}=\{[(x_{i},  x'_{0}),  1],  [(x_{i},
  x'_{1}),   1],   \dots,   [(x_{i},   x'_{P}),  1]\}$,  where  $P$  is  also  a
  hyperparameter  set  by  us  that  controls  the number of sentences we should
  sample from each class.

@@

  In  this  way,  we  can generate the sentence pair dataset $\mathcal{D'}$ for
  stage  2 based on the top-K class label set $\mathcal{C'}$ provided by stage 1
  as   $\mathcal{D'}=\{\mathcal{P'}_{i}\cup   \mathcal{N'}_{i}\}_{i=1}^{N}$,  in
  which we will have $M=N\cdot K\cdot P$ data points of sentence pairs in total.

@@

  As for  stage  1,  our  two-stage SFC  system  can adapt to any auxiliary model or even
  searching  tool  based  on  Term Frequency-Inverse Document Frequency (TF-IDF)
  retrieval.  In  this  paper,  however,  we  choose to fine-tune pretrained model such as RoBERTa on our
  task-specific  dataset $\mathcal{D}$ by adding a softmax classifier on top of
  it for better
  overall  performance.  According  to  our  experimental  result,  RoBERTa  can
  guarantee  that  approximately  95\%  ground  truth labels be included in top-5
  candidate  class  labels  with  highest  probability if it has been fine-tuned on
  task-specific  dataset and can obtain a well performance measured by F-score over
  0.75 on this dataset.  So  we use RoBERTa as the encoder of classification model in our setting at
  stage 1 to ensure low limitation for the performance of stage 2.

  For single-sentence text classification tasks, given a data point $x_{i}$ with
  class  label  $y_{i}$  from  dataset  $\mathcal{D}$, RoBERTa takes the final
  hidden  state  $h_{i}$  of the first token [CLS] as the representation for the
  whole   sequence  of  $x_{i}$.  Let's  suppose  we  have  a  linear  layer  as
  ${\Phi}^C_{i}=W^Ch_{i}+b^C$,  where  $W^C$ and $b^C$ are trainable parameters,
  the    probability    score    for    $x_{i}$    can    be    calculated    as
  $p^C_{i}=softmax(W^Ch_{i}+b^C)=softmax({\Phi}^C_{i})$.   Then,  the  loss  for
  stage 1 classification model is shown in Equ. \ref{eq:classification loss}, in
  which  the  first  term  $\varPhi_{i,y_{i}}^C$ encourages high probability for
  prediction of the correct label $y_{i}$.

@@

  As for  stage 2, we also choose RoBERTa as the encoder for the sentence pair similarity model. Before sending sentence pairs to Roberta, we
  pack  sentence  pairs  into a single sequence and separate them with a special
  token  [SEP].  Roberta  will  also  add  a  learned  embedding  to every token
  indicating  whether  it belongs to the first sentence or the second one. Then,
  we  utilize  the  cross-attention  mechanism  inside RoBERTa, and then extract
  semantic relationship between 2 sentences from the output softmax layer, which
  is placed on top of the last hidden representation of the [CLS] token.

@@

  Due  to  the  fact that sentence pairs within the same class is much less than
  sentence  pairs  from  different  classes,  the  dataset  $\mathcal{D'}$  is
  imbalanced.  Therefore, we will accommodate a weight variable $w^S = [K-1, 1]$
  to  the  loss  to eliminate the bias brought by imbalanced data, shown in Equ.
  \ref{eq:similarity loss}.

@@

  As  for top-K classification task, it shares the same sentence pair similarity
  model   structure  with  task  1.  The  only  difference  is  that  we  add  a
  task-specific  average  pooling  layer,  shown  in  Fig.  \ref{fig:framework} to
  implement the classification task based on sentence-pair model.

@@

  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason for giving task 2 relatively more weights is that according to the ablation experiments we did in Section \ref{sec:exp}, task 2 contributes more to the overall performance.

@@

  \begin{table*}
    \begin{centering}
      \scalebox{0.9}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} & \textbf{\#Samples} & \textbf{\#Samples/Class} & \textbf{Experimental Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 & 17 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 1942 & 8 & class sampling\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
      \end{tabular}
      }
    \par
    \end{centering}
    \caption{Key statistics for experimental datasets and few shot settings}

@@

  \section{Experiments}
  \label{sec:exp}

  In  this  section,  we  conduct  extensive  experiments  over  5 task-specific
  datasets  to  evaluate  the  performance  of  our  proposed SFC system and the
  effectiveness  of  the  methodology  of  multi-task  learning  and
  joint-model structure under low-data settings.

  \subsection{Datasets}
  The  datasets  used in our experiments aims to help us study low-resource text
  classification  problem  under  task-specific conversational chatbot scenario.
  Therefore,  we did experiments on datasets under low-resource chatbot corpus setting,
  which  is a large number of class labels (50-250) with a few examples(5-20) in
  short  text  for  each  class, by sampling smaller subsets from the full scale
  when the raw datasets are oversized, see Table \ref{tbe:dataset statistic}. Besides, we also did extensive experiments with larger scale datasets with 30-50 examples per class to test the stability of our proposed SFC system under normal-size data settings, also see Table \ref{tbe:dataset statistic}.

@@

  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
  classification  task from the extreme classification repository with full data
  containing  670,091  class  labels,  285,176  training samples and 150875 test
  samples \cite{bhatia2016extreme}.  As  the  dataset  contains  multiple class
  labels  per  training sample, we keep only the first class label for each data
  point. Besides, we also randomly sampled 250 class labels from all the classes
  that  contain only 5-15 data points. In this way, we simulate the low-resource
  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
  samples for 250 class labels.

@@

      \scalebox{0.55}{
        \begin{tabular}{|c|cccccc|cccccc|cccccc|c|c|}

@@

          \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{6}{c|}{\textbf{CLINC150}}& \multicolumn{6}{c|}{\textbf{BANKING77}}& \multicolumn{6}{c|}{\textbf{HWU64}}& \ \ \ \textbf{ITG} \ \ \ & \textbf{Amazon-670k}\tabularnewline
          \cline{2-21}
          \multicolumn{1}{|c|}{} & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & $\textbf{5}$ & $\textbf{10}$ & $\textbf{15}$ & $\textbf{20}$ & $\textbf{30}$ & $\textbf{50}$ & \textbf{Full} & \textbf{Full}\tabularnewline

@@

          TextCNN & \multirow{2}*{$0.5318$} & \multirow{2}*{$0.6963$} & \multirow{2}*{$0.7609$} & \multirow{2}*{$0.8142$} & \multirow{2}*{$0.8526$} & \multirow{2}*{$0.8867$} & \multirow{2}*{$0.4408$} & \multirow{2}*{$0.6436$} & \multirow{2}*{$0.7366$} & \multirow{2}*{$0.7918$} & \multirow{2}*{$0.8228$} & \multirow{2}*{$0.8619$} & \multirow{2}*{$0.3112$} & \multirow{2}*{$0.4007$} & \multirow{2}*{$0.4823$} & \multirow{2}*{$0.5272$} & \multirow{2}*{$0.5782$} & \multirow{2}*{$0.6262$} & \multirow{2}*{$0.6624$} & \multirow{2}*{$0.4401$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          LEAM & \multirow{2}*{$0.7514$} & \multirow{2}*{$0.8203$} & \multirow{2}*{$0.8612$} & \multirow{2}*{$0.8802$} & \multirow{2}*{$0.9010$} & \multirow{2}*{$0.9180$} & \multirow{2}*{$0.5422$} & \multirow{2}*{$0.7812$} & \multirow{2}*{$0.8129$} & \multirow{2}*{$0.8280$} & \multirow{2}*{$0.8610$} & \multirow{2}*{$0.8727$} & \multirow{2}*{$0.4545$} & \multirow{2}*{$0.5554$} & \multirow{2}*{$0.5936$} & \multirow{2}*{$0.6599$} & \multirow{2}*{$0.6855$} & \multirow{2}*{$0.7046$} & \multirow{2}*{$0.7086$} & \multirow{2}*{$0.6091$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          BERT-large & \multirow{2}*{$0.8080$} & \multirow{2}*{$0.8904$} & \multirow{2}*{$0.9265$} & \multirow{2}*{$0.9334$} & \multirow{2}*{$0.9497$} & \multirow{2}*{$0.9595$} & \multirow{2}*{$0.5780$} & \multirow{2}*{$0.8004$} & \multirow{2}*{$0.8518$} & \multirow{2}*{$0.8827$} & \multirow{2}*{$0.8858$} & \multirow{2}*{$0.8982$} & \multirow{2}*{$0.4711$} & \multirow{2}*{$0.5963$} & \multirow{2}*{$0.6342$} & \multirow{2}*{$0.7010$} & \multirow{2}*{$0.7117$} & \multirow{2}*{$0.7424$} & \multirow{2}*{$0.7485$} & \multirow{2}*{$0.6658$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          ALBERT-xxlarge & \multirow{2}*{$0.8497$} & \multirow{2}*{$0.9008$} & \multirow{2}*{$0.9296$} & \multirow{2}*{$0.9297$} & \multirow{2}*{$0.9466$} & \multirow{2}*{$0.9578$} & \multirow{2}*{$0.5549$} & \multirow{2}*{$0.7981$} & \multirow{2}*{$0.8231$} & \multirow{2}*{$0.8530$} & \multirow{2}*{$0.8571$} & \multirow{2}*{$0.9096$} & \multirow{2}*{$0.4879$} & \multirow{2}*{$0.6116$} & \multirow{2}*{$0.6135$} & \multirow{2}*{$0.6996$} & \multirow{2}*{$0.7094$} & \multirow{2}*{$0.7376$} & \multirow{2}*{$0.7253$} & \multirow{2}*{$0.6893$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-base & \multirow{2}*{$0.8732$} & \multirow{2}*{$0.9254$} & \multirow{2}*{$0.9363$} & \multirow{2}*{$0.9482$} & \multirow{2}*{$0.9558$} & \multirow{2}*{$0.9637$} & \multirow{2}*{$0.7305$} & \multirow{2}*{$0.8654$} & \multirow{2}*{$0.8808$} & \multirow{2}*{$0.9080$} & \multirow{2}*{$0.9061$} & \multirow{2}*{$0.9293$} & \multirow{2}*{$0.5831$} & \multirow{2}*{$0.6790$} & \multirow{2}*{$0.7064$} & \multirow{2}*{$0.7100$} & \multirow{2}*{$0.7320$} & \multirow{2}*{$0.7472$} & \multirow{2}*{$0.7734$} & \multirow{2}*{$0.6708$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$0.8974$} & \multirow{2}*{$0.9372$} & \multirow{2}*{$0.9508$} & \multirow{2}*{$0.9584$} & \multirow{2}*{$0.9621$} & \multirow{2}*{$0.9733$} & \multirow{2}*{$0.7690$} & \multirow{2}*{$0.8728$} & \multirow{2}*{$0.8966$} & \multirow{2}*{$0.9099$} & \multirow{2}*{$0.9227$} & \multirow{2}*{$0.9313$} & \multirow{2}*{$0.6044$} & \multirow{2}*{$0.7002$} & \multirow{2}*{$0.7129$} & \multirow{2}*{$0.7436$} & \multirow{2}*{$0.7493$} & \multirow{2}*{$0.7678$} & \multirow{2}*{$0.7990$} & \multirow{2}*{$0.7156$}\tabularnewline
          (classification) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          RoBERTa-large & \multirow{2}*{$0.8266$} & \multirow{2}*{$0.8861$} & \multirow{2}*{$0.9023$} & \multirow{2}*{$0.9084$} & \multirow{2}*{$0.9090$} & \multirow{2}*{$0.9407$} & \multirow{2}*{$0.757$} & \multirow{2}*{$0.8476$} & \multirow{2}*{$0.8614$} & \multirow{2}*{$0.8743$} & \multirow{2}*{$0.8749$} & \multirow{2}*{$0.8980$} & \multirow{2}*{$0.5425$} & \multirow{2}*{$0.6164$} & \multirow{2}*{$0.6503$} & \multirow{2}*{$0.6729$} & \multirow{2}*{$0.6947$} & \multirow{2}*{$0.7231$} & \multirow{2}*{$0.7418$} & \multirow{2}*{$0.6362$}\tabularnewline
          (similarity) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.9591$} & \multirow{2}*{$0.9610$} & \multirow{2}*{$0.9664$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.9187$} & \multirow{2}*{$0.9198$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7484$} & \multirow{2}*{$0.7653$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline
          (task1 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

    \label{tbe:table2}
  \end{table*}
